A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-04-21 doc/paper.tex
Reordering section 3. Fixes #53.

	\section{Approach/Methodology} \subsection{Walkthrough of Tool} Before
	discussing the minutiae of how the tool was developed, it will help first to
	give a basic example of how the tool can be used and how to interpret its
	symbols. One such example might be to find the answer to this question:
	\textit{ What kinds of functions do people use to define the condition in an IF
		function?} The final visualization is available in figure \ref{fig:fullpic};
	however, to understand the interaction, we will start rather from the
	beginning. \par

>>>>

	\section{Approach/Methodology}

	\subsection{Walkthrough of Tool} Before
	discussing the minutiae of how the tool was developed, it will help first to
	give a basic example of how the tool can be used and how to interpret its
	symbols. One such example might be to find the answer to this question:
	\textit{ What kinds of functions do people use to define the condition in an IF
		function?} The final visualization is available in figure \ref{fig:fullpic};
	however, to understand the interaction, we will start rather from the
	beginning. \par
